\LARGE \bf Predicting Initialization Effectiveness for Trajectory Optimization

### 2014-02-14 paper.tex
small
changes

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{bm}
\usepackage[caption=false]{subfig}
\usepackage{algpseudocode}
\usepackage[table]{xcolor}

@@

Robotic motion planning problems can be formulated as non-convex optimization problems, i.e., minimize an objective subject to inequality and equality constraints:
\begin{align}
\label{eq:opt}
& \underset{\x}{\text{minimize}}
& & f(\x) \\
& \text{subject to}
& & g_i(\x) \leq 0, \; i = 1, 2, \dots, n_{\text{ieq}} \notag \\
&&& h_i(\x) = 0, \; i = 1, 2, \dots, n_{\text{eq}} \notag
\end{align}
where $f$, $g_i$ and $h_i$ are scalar functions. For planning problems that involve only kinematics and represent the trajectory as a sequence of $T$ waypoints, the optimization variable $\x$ is of the form $\x = \btheta_{1:T}$, where $\btheta_t \in \mathbb{R}^K$ denotes the configuration at the $t$-th waypoint for a system with $K$ degrees of freedom. For problems with dynamics, the optimization variable $\x$ may also include velocities $\dot{\btheta_t}$ and torques ${\bm \tau}_t$.

@@

Before extracting features from a trajectory, we first perform re-sampling on it so that waypoints are uniformly distributed between two end-points.
We perform this pre-processing based on what was pointed out by Ratliff et al.~\cite{Ratliff:2009:CGO}: the objective function should be invariant to the re-parameterization of the trajectory so that the gradient will pull a trajectory out of obstacles instead of encouraging it to quickly jump through obstacles. Some recent work such as~\cite{Schulman:2013:FLO} handles the `jumping through problem' in a completely different way, but in practice, it is observed that a re-sampling pre-processing can still result in better convergence. 
The re-sampling process removes some the parameterization-dependent differences between trajectories and hence makes it easier to compare them. After re-sampling, each trajectory has $T$ waypoints. This also results in fixed-length feature vectors.

@@

\begin{figure}[!h]
\centering
\subfloat[]{\includegraphics[width=0.52\linewidth]{figure/penetration_encode.pdf}}
\subfloat[]{\includegraphics[width=0.47\linewidth]{figure/discrete_directions.pdf}}
\caption{Spatial signed distance vectors: (a) shows a 2D example about SSD vector generation. The surrounding space around a robot link (the cyan color part) is uniformly divided by a spatial vector dictionary with $12$ directions $\{\mathbf b_1, ..., \mathbf b_{12}\}$. The signed distance value $\text{sd}_j$ between the robot and the $j$-th obstacle (the grey part) is then accumulated toward a direction $\mathbf b_k$, which has the smallest angle with the corresponding signed distance normal $\mathbf n_j$, i.e., with the smallest $|\mathbf n_j \cdot \mathbf b_k|$. (b) In 3D case, we use the approach introduced in~\cite{Yershova:2010:GUI} to generate dictionary vectors that make equisurface partition on a sphere surface. }
\label{fig:trajectoryfeaturePD}
\end{figure}

@@

\subsection{Feature IV: Convexity Features}
As another category of features, we also measure the local convexity of the trajectory optimization problem around the initial trajectory. 
The optimization problem formalized in Equation~\ref{eq:opt} usually involves non-convex objective and constraints. In trajectory optimization algorithms, these non-convex terms are approximated by convex functions in each iteration of the optimization. The convexity features quantify how close the approximations are in such `convexify' steps.

We first compute Hessian matrices of the objective and constraint functions at the trajectory. Next, to measure the local non-convexity of the optimization problem, we compute the following features based on the eigenvalues of the Hessian matrices: (i) the minimum eigenvalue; (ii) the sum of negative eigenvalues; (iii) the maximum eigenvalue; (iv) the sum of all eigenvalues. We compute these four statistics for each objective and constraint function, and generate a total of $4 times T \times (1 + n_{\text{ieq}} + n_{\text{eq}})$ convexity features, which are collected in a feature vector denoted as $\fconv$.

@@

\subsection{Experiment Setting}
For each benchmark, we have a pre-defined set of task settings (the initial and goal configurations) as seed tasks. For PR2 benchmarks, we use the $198$ arm planning problems and $96$ full-body problems used in TrajOpt~\cite{Schulman:2013:FLO}. For dubins car benchmarks, we manually select a set of initial-goal configurations that should have feasible solutions. Next, we perturb the initial and goal configurations around these seed tasks to generate more random tasks. We filter out the invalid tasks where the initial or goal configurations are in-collision. We also remove the trivial cases where the linear interpolation between initial and goal is collision-free. We did not randomly select tasks in the entire configuration space because this will incorrectly bias the classifier toward tasks that will hardly happen in real world robotics applications.

Given one planning task, we first generate a trajectory which is a simple linear interpolation between the initial and goal configurations. Next, we perform random perturbation of the trajectory waypoints and generate more random trajectories. For each of these trajectories, we run the trajectory optimization algorithm using it as the initial guess. When the optimization stops, we will obtain a sequence of trajectories. These intermediate trajectories can also be used as initializer and they would all have the same effectiveness label as the actual initial guess. As a result, if the optimization converges and the final outcome is feasible, we evaluate the given initial trajectory and all intermediate trajectories as `good' initializations. Otherwise we evaluate all of them as `bad'. Finally, we extract features for all these labeled trajectories and add them into the dataset. In this way, we generate more than $10,000$ trajectories for each planning benchmark. For each benchmark, we use half of the data for training a classifier and the rest for testing experiments. When splitting training and test sets, we make sure that trajectories corresponding to the same task are assigned into the same set, in order to guarantee that the test set is independent of the training set. In Figure~\ref{fig:features}, we visualize the features of two trajectories from different benchmarks. Except $\fconv$, all these features can be computed in less than 10 milleseconds per trajectory. $\fconv$ is more expensive (several seconds) since it is time consuming to compute a trajectory's Hessian matrix numerically.

\subsection{Effectiveness Prediction on Same Benchmarks}
We first show the prediction accuracy when using a classifier learned on one benchmark to predict the effectiveness of trajectories in the same benchmark but for different tasks. The results are shown in Table~\ref{tab:result}, where we compare the baseline accuracy and the accuracy when different combinations of features are used to train a classifier. From the results, we observe that the learned classifiers provide accuracy significantly higher than the baseline (which simply predicts according to the majority label in the training set). However, the peak accuracy may be achieved by different combination of features on different benchmarks.

@@

There are several reasons for the poor transfer performance of the current prediction algorithm. First, our current feature design only considers the spatial information locally around the trajectory and does not take into account the global description about the environment, which has been proved to be helpful for trajectory transferring between different environments~\cite{Jetchev:2013:FMP}. For instance, the classifier learned on squared-dubin in Figure~\ref{fig:benchmarks1}(c) can be successfully transferred to jagged-dubin in Figure~\ref{fig:benchmarks1}(a) because the environments are similar. The transfer to gap-dubin in Figure~\ref{fig:benchmarks1}(b) is difficult because the existence of the narrow gap, which does not exist in squared-dubin or jagged dubin benchmark. Second, a high-DOF robot may use different part of DOFs in different scenarios; this results in different trajectory distributions on different benchmarks. Hence, we need more trajectory data from various scenarios and tasks, in order to completely cover the trajectory space. Finally, the rotation-invariance of features is also important for transferring. From the successful case shown in Table~\ref{tab:result2}, we observe that the feature combination $\fcon+\fsht$ behaves the best in transferring, and both of them are rotation-invariant features.

\begin{figure*}[t]
\centering
\includegraphics[width=0.8\linewidth]{figure/features.pdf}
\caption{Features for two different trajectories in the bookshelf benchmark. Rough periods appears for all the three sub-features $\fssd$, $\fcon$ and $\fsht$, because these features are computed for each trajectory waypoint.}
\label{fig:features}
\end{figure*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|r|r|r|}
\hline 
 & baseline & ${\bf z}_\textrm{conv} +\fssd+\fcon+\fsht$  & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin & 59.2 & 90.2  & 82.6	& 82.2 & 74.7 & 82.3 & 82.2 & 70.1 & 63.15 \\ \hline
gap-dubin & 56.4 & 90.5 & 88.6 & 87.9 & 77.3 & 86.2 & 87.1 & 76.2 & 76.0 \\ \hline
squared-dubin & 56.8 & 98.3 & 89.3 & 	87.1 & 	77.5 &	88.2 &	85.0 &	 61.7	& 61.5 \\ \hline \hline

bookshelf & 63.0 & 100 & 77.7 & 	77.5 &	73.9 &	77.5 &	76.3 &	68.7 & 70.0 \\ \hline
skew-bookshelf & 62.1 & 85.9 & 80.4 &	74.3 & 	77.9 & 	76.2 &	72.3 &	63.7 &	65.0 \\ \hline
countertop & 69 & 99.7 & 70.1	& 72.8 & 	74.5	 & 69.6 & 	73.9 &	77.7 &	63.6 \\ \hline
industrial & 67.2 & 83.8 & 78.5 &	78.2 &	78.4 &	78.2 &	76.9 &	80.2 & 	73.7 \\ \hline
industrial2 & 50.3 & 96.2 & 61.1 & 	62.1	 & 64.1 &	61.2 & 	62.3 & 	64.5 &	58.2 \\ \hline \hline

livingroom & 61.0 & & 85.5	& 88.4 &	 83.6 &	84.7 &	87.4 & 	82.8 &	81.6 \\ \hline
livingroom2 & 53.7 & & 80.3 &	 80.5	& 76.7 &	 78.6 &	77.9 & 	71.5 & 	66.6 \\ \hline
kitchen & 59.0 & & 65 & 	64.2 & 	60.4 &	66.9 & 	66.2 & 	60.3 & 	73.6 \\ \hline
kitchen2 & 54.0 & & 64.6 &	65.3 & 	61.6 & 	65.0 & 	65.0 & 	61.0 &	61.5 \\ \hline
hotel & 98 & & 98.1 &	98.1 & 	98.2 &	98.1 &	98.1 &	97	& 98.1 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%): We compare the prediction accuracy of the baseline (i.e., the percentage of majority trajectory label) with the prediction results when using all the features we designed $\fssd+\fcon+\fsht$ and other combinations of features.}
\label{tab:result}
\end{table*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|r|r|r|r|r|r|r|r|r|}
\hline 
 & baseline &  ${\bf z}_\textrm{conv} +\fssd+\fcon+\fsht$ & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin to squared-dubin &  56.8 & 88.8 & 49.7 & 49.0 &	74.4 & 	56.9 & 	60.3	 & 67.9	& 55.5
 \\ \hline
squared-dubin to jagged-dubin & 59.2 & 58.9 & 56.9 &	56.8 &	71.1 & 	56.9 &	56.9 &	61.2 &	63.8 \\ \hline
bookshelf to skew-bookshelf & 62.1 & 86.7 & 57.1 &	59.4 &	82.1 & 	53.2 &	57.3 &	60.3 &	67.4 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) when applying the classifier learned on one benchmark onto trajectories from other benchmarks. The baseline is the percentage of majority trajectory label of the benchmark where the classifier is transferred to.}
\label{tab:result2}
\end{table*}

@@

\section*{Acknowledgments}
This research has been funded in part by Darpa Young Faculty Award \#D13AP00046, and by a Sloan Fellowship.

>>>>

% The following packages can be found on http:\\www.ctan.org
\usepackage{graphics} % for pdf, bitmapped graphics files
\usepackage{epsfig} % for postscript graphics files
%\usepackage{mathptmx} % assumes new font selection scheme installed
%\usepackage{times} % assumes new font selection scheme installed
\usepackage{amsmath} % assumes amsmath package installed
\usepackage{amssymb}  % assumes amsmath package installed
\usepackage{bm}
\usepackage[caption=false]{subfig}
\usepackage{algpseudocode}
\usepackage[table]{xcolor}
\usepackage{array}
\newcommand{\PreserveBackslash}[1]{\let\temp=\\#1\let\\=\temp}
\newcolumntype{C}[1]{>{\PreserveBackslash\centering}p{#1}}
\newcolumntype{R}[1]{>{\PreserveBackslash\raggedleft}p{#1}}
\newcolumntype{L}[1]{>{\PreserveBackslash\raggedright}p{#1}}

@@

\subsection{Background}
Robotic motion planning problems can be formulated as non-convex optimization problems, i.e., minimize an objective subject to inequality and equality constraints:
\begin{align}
\label{eq:opt}
& \underset{\x}{\text{minimize}}
& & f(\x) \\
& \text{subject to}
& & g_i(\x) \leq 0, \; i = 1, 2, \dots, n_{\text{ieq}} \notag \\
&&& h_i(\x) = 0, \; i = 1, 2, \dots, n_{\text{eq}} \notag
\end{align}
where $f$, $g_i$ and $h_i$ are scalar functions. For planning problems that involve only kinematics and represent the trajectory as a sequence of $T$ waypoints, the optimization variable $\x$ is of the form $\x = \btheta_{1:T}$, where $\btheta_t \in \mathbb{R}^K$ denotes the configuration at the $t$-th waypoint for a system with $K$ degrees of freedom. For problems with dynamics, the optimization variable $\x$ may also include velocities $\dot{\btheta_t}$ and torques ${\bm \tau}_t$.

@@

Before extracting features from a trajectory, we first perform re-sampling on it so that waypoints are uniformly distributed between two end-points.
%We perform this pre-processing based on what was pointed out by Ratliff et al.~\cite{Ratliff:2009:CGO}: the objective function should be invariant to the re-parameterization of the trajectory so that the gradient will pull a trajectory out of obstacles instead of encouraging it to quickly jump through obstacles. Some recent work such as~\cite{Schulman:2013:FLO} handles the `jumping through problem' in a completely different way, but in practice, it is observed that a re-sampling pre-processing can still result in better convergence. 
The re-sampling process removes some the parameterization-dependent differences between trajectories and hence makes it easier to compare them. After re-sampling, each trajectory has $T$ waypoints. This also results in fixed-length feature vectors.

@@

\begin{figure}[!h]
\centering
\subfloat[]{\includegraphics[width=0.42\linewidth]{figure/penetration_encode.pdf}} \qquad
\subfloat[]{\includegraphics[width=0.38\linewidth]{figure/discrete_directions.pdf}}
\caption{Spatial signed distance vectors: (a) shows a 2D example about SSD vector generation. The surrounding space around a robot link (the cyan color part) is uniformly divided by a spatial vector dictionary with $12$ directions $\{\mathbf b_1, ..., \mathbf b_{12}\}$. The signed distance value $\text{sd}_j$ between the robot and the $j$-th obstacle (the grey part) is then accumulated toward a direction $\mathbf b_k$, which has the smallest angle with the corresponding signed distance normal $\mathbf n_j$, i.e., with the smallest $|\mathbf n_j \cdot \mathbf b_k|$. (b) In 3D case, we use the approach introduced in~\cite{Yershova:2010:GUI} to generate dictionary vectors that make equisurface partition on a sphere surface. }
\label{fig:trajectoryfeaturePD}
\end{figure}

@@

\subsection{Feature IV: Convexity Features}
As another category of features, we also measure the local convexity of the trajectory optimization problem around the initial trajectory. 
The optimization problem formalized in Equation~\ref{eq:opt} usually involves a non-convex objective and non-convex constraints. In trajectory optimization algorithms, these non-convex terms are approximated by convex functions in each iteration of the optimization. The convexity features quantify how close the approximations are in such `convexify' steps.

We first compute Hessian matrices of the objective and constraint functions at the trajectory. Next, to measure the local non-convexity of the optimization problem, we compute the following features based on the eigenvalues of the Hessian matrices: (i) the minimum eigenvalue; (ii) the sum of negative eigenvalues; (iii) the maximum eigenvalue; (iv) the sum of all eigenvalues. We compute these four statistics for each objective and constraint function, and generate a total of $4 \times T \times (1 + n_{\text{ieq}} + n_{\text{eq}})$ convexity features, which are collected in a feature vector denoted as $\fconv$.

@@

\subsection{Experimental Setting}

For each benchmark, we have a pre-defined set of task settings (the initial and goal configurations) as seed tasks. For the PR2 benchmarks, we use the $198$ arm planning problems and $96$ full-body problems used in TrajOpt~\cite{Schulman:2013:FLO}. For the Dubins car benchmarks, we manually select a set of initial-goal configurations that should have feasible solutions. Next, we perturb the initial and goal configurations around these seed tasks to generate more random tasks. We filter out the invalid tasks where the initial or goal configurations are in-collision. We also remove the trivial cases where the linear interpolation between initial and goal is collision-free. We did not randomly select tasks in the entire configuration space because this will incorrectly bias the classifier toward tasks that will hardly happen in real world robotics applications.

Given one planning task, we first generate a trajectory which is a simple linear interpolation between the initial and goal configurations. Next, we perform random perturbation of the trajectory waypoints and generate more random trajectories. For each of these trajectories, we run the trajectory optimization algorithm using it as the initial guess. When the optimization stops, we will obtain a sequence of trajectories. These intermediate trajectories can also be used as initializer and they would all have the same effectiveness label as the actual initial guess. As a result, if the optimization converges and the final outcome is feasible, we evaluate the given initial trajectory and all intermediate trajectories as `good' initializations. Otherwise we evaluate all of them as `bad'. Finally, we extract features for all these labeled trajectories and add them into the dataset. In this way, we generate more than $10,000$ trajectories for each planning benchmark. For each benchmark, we use half of the data for training a classifier and the rest for testing experiments. When splitting training and test sets, we make sure that trajectories corresponding to the same task are assigned into the same set, in order to guarantee that the test set is independent of the training set. In Figure~\ref{fig:features}, we visualize the features of two trajectories from different benchmarks. Except $\fconv$, all these features can be computed in less than 10 milleseconds per trajectory. $\fconv$ is more expensive (about 8 seconds) since it is time consuming to compute a trajectory's Hessian matrix numerically.

\subsection{Effectiveness Prediction on Same Benchmarks}
We first show the prediction accuracy when using a classifier learned on one benchmark to predict the effectiveness of trajectories in the same benchmark but for different tasks. The results are shown in Table~\ref{tab:result}, where we compare the baseline accuracy and the accuracy when different combinations of features are used to train a classifier. From the results, we observe that the learned classifiers provide accuracy significantly higher than the baseline (which simply predicts according to the majority label in the training set). However, the peak accuracy may be achieved by a different combination of features on different benchmarks.

@@

There are several reasons for the poor transfer performance of the current prediction algorithm. First, our current feature design only considers the spatial information locally around the trajectory and does not take into account the global description about the environment, which has been proved to be helpful for trajectory transferring between different environments~\cite{Jetchev:2013:FMP}. For instance, the classifier learned on squared-Dubin in Figure~\ref{fig:benchmarks1}(c) can be successfully transferred to jagged-dubin in Figure~\ref{fig:benchmarks1}(a) because the environments are similar. The transfer to gap-dubin in Figure~\ref{fig:benchmarks1}(b) is difficult because the existence of the narrow gap, which does not exist in the squared-dubin or jagged-dubin benchmark.  Second, a high-DOF robot may use different part of DOFs in different scenarios; this results in different trajectory distributions on different benchmarks. Hence, we need more trajectory data from various scenarios and tasks, in order to completely cover the trajectory space. Finally, the rotation-invariance of features is also important for transferring. From the successful case shown in Table~\ref{tab:result2}, we observe that the feature combination $\fcon+\fsht$ behaves the best in transferring, and both of them are rotation-invariant features.

\begin{figure*}[t]
\centering
\includegraphics[width=0.76\linewidth]{figure/features.pdf}
\caption{$\fssd$, $\fcon$ and $\fsht$ features for two different trajectories in the bookshelf benchmark. Rough periods appears for all the three sub-features, because these features are computed for each trajectory waypoint.}
\label{fig:features}
\end{figure*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|R{0.9cm}|R{1.5cm}|R{1.3cm}|R{1.2cm}|R{1.2cm}|R{1.2cm}|R{0.9cm}|R{0.9cm}|R{0.9cm}|}
\hline 
 & baseline & $\fconv +\fssd+\fcon+\fsht$  & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin & 59.2 & 90.2  & 82.6	& 82.2 & 74.7 & 82.3 & 82.2 & 70.1 & 63.15 \\ \hline
gap-dubin & 56.4 & 90.5 & 88.6 & 87.9 & 77.3 & 86.2 & 87.1 & 76.2 & 76.0 \\ \hline
squared-dubin & 56.8 & 98.3 & 89.3 & 	87.1 & 	77.5 &	88.2 &	85.0 &	 61.7	& 61.5 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) for the Dubins car planning: We compare the prediction accuracy of the baseline (i.e., the percentage of majority trajectory label) with the prediction results when using all the features we designed $\fconv+\fssd+\fcon+\fsht$ and other combinations of features.}
\label{tab:result-dubins}
\end{table*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|R{0.9cm}|R{1.5cm}|R{1.3cm}|R{1.2cm}|R{1.2cm}|R{1.2cm}|R{0.9cm}|R{0.9cm}|R{0.9cm}|}
\hline 
 & baseline & $\fconv +\fssd+\fcon+\fsht$  & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
bookshelf & 63.0 & 100 & 77.7 & 	77.5 &	73.9 &	77.5 &	76.3 &	68.7 & 70.0 \\ \hline
skew-bookshelf & 62.1 & 85.9 & 80.4 &	74.3 & 	77.9 & 	76.2 &	72.3 &	63.7 &	65.0 \\ \hline
countertop & 69 & 99.7 & 70.1	& 72.8 & 	74.5	 & 69.6 & 	73.9 &	77.7 &	63.6 \\ \hline
industrial & 67.2 & 83.8 & 78.5 &	78.2 &	78.4 &	78.2 &	76.9 &	80.2 & 	73.7 \\ \hline
industrial2 & 50.3 & 96.2 & 61.1 & 	62.1	 & 64.1 &	61.2 & 	62.3 & 	64.5 &	58.2 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) for PR2 arm planning: We compare the prediction accuracy of the baseline (i.e., the percentage of majority trajectory label) with the prediction results when using all the features we designed $\fconv+\fssd+\fcon+\fsht$ and other combinations of features.}
\label{tab:result-arm}
\end{table*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|R{0.9cm}|R{1.5cm}|R{1.3cm}|R{1.2cm}|R{1.2cm}|R{1.2cm}|R{0.9cm}|R{0.9cm}|R{0.9cm}|}
\hline 
 & baseline  & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
livingroom & 61.0 & 85.5	& 88.4 &	 83.6 &	84.7 &	87.4 & 	82.8 &	81.6 \\ \hline
livingroom2 & 53.7 & 80.3 &	 80.5	& 76.7 &	 78.6 &	77.9 & 	71.5 & 	66.6 \\ \hline
kitchen & 59.0 & 65 & 	64.2 & 	60.4 &	66.9 & 	66.2 & 	60.3 & 	73.6 \\ \hline
kitchen2 & 54.0 & 64.6 &	65.3 & 	61.6 & 	65.0 & 	65.0 & 	61.0 &	61.5 \\ \hline
hotel & 98 & 98.1 &	98.1 & 	98.2 &	98.1 &	98.1 &	97	& 98.1 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) for PR2 fullbody planning: We compare the prediction accuracy of the baseline (i.e., the percentage of majority trajectory label) with the prediction results when using features $\fssd+\fcon+\fsht$ and other combinations of features.}
\label{tab:result}
\end{table*}

\begin{table*}[tbp]
\rowcolors{1}{gray!25}{}
\centering
\begin{tabular}{|c|R{0.9cm}|R{1.5cm}|R{1.3cm}|R{1.2cm}|R{1.2cm}|R{1.2cm}|R{0.7cm}|R{0.7cm}|R{0.7cm}|}
\hline 
 & baseline & $\fconv +\fssd+\fcon+\fsht$ & $\fssd+\fcon+\fsht$ & $\fssd+\fcon$ & $\fcon+\fsht$ & $\fssd+\fsht$ & $\fssd$ & $\fcon$ & $\fsht$ \\ \hline \hline
jagged-dubin to squared-dubin &  56.8 & 88.8 & 49.7 & 49.0 &	74.4 & 	56.9 & 	60.3	 & 67.9	& 55.5
 \\ \hline
squared-dubin to jagged-dubin & 59.2 & 58.9 & 56.9 &	56.8 &	71.1 & 	56.9 &	56.9 &	61.2 &	63.8 \\ \hline
bookshelf to skew-bookshelf & 62.1 & 86.7 & 57.1 &	59.4 &	82.1 & 	53.2 &	57.3 &	60.3 &	67.4 \\ \hline
\end{tabular}
\caption{Effectiveness prediction accuracy (in \%) when applying the classifier learned on one benchmark onto trajectories from other benchmarks. The baseline is the percentage of majority trajectory label of the benchmark where the classifier is transferred to.}
\label{tab:result2}
\end{table*}

@@

\section*{Acknowledgments}
This research has been funded in part by Darpa Young Faculty Award \#D13AP00046 and by a Sloan Fellowship.
